Queue Aware Precoder Design for Space Frequency Resource Allocation

### 2014-07-03 Report/kkt_mse_approach.tex
17.28:00 Jul-03-2014

So far, we have discussed the problem of minimizing the number of backlogged packets at the \acp{BS} using the precoders by formulating it as an optimization problem, which can be handled by the existing solvers CVX \cite{grant2008cvx}. In this section, we provide an iterative precoder design for the \ac{JSFRA} formulation approached via \ac{MSE} reformulation as discussed in \ref{sec-3.3}. Even though the \ac{JSFRA} scheme using \ac{SCA} approach and the \ac{MSE} reformulation approach obtained the solutions by relaxing the nonconvex constraints by the half spaces, the structure of the \ac{MSE} reformulation problem allows us to decouple the problem readily without further approximations.

In order to come up with the iterative solution, we need to find the \ac{KKT} equations for the the \ac{MSE} reformulation problem defined in \eqref{eqn-mse-2}. It can be seen that the objective function \eqref{eqn-mse-2.1} has the norm function, which requires the sum of absolute values of the vector entries raised to the power \me{q}. Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach. Since the subgradients are not unique and the selection of a subgradient and a step size are not guaranteed to be optimal, in this approach, we drop the absolute value operation for the queue deviation function so as to obtain a unique supporting vector. It is valid in the following special cases without affecting the optimal solution
\begin{itemize}
\item when the exponent \me{q} is odd and \me{q > 1} or,
\item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
\end{itemize}
The first condition is from the fact that the differential of a function with power \me{q} leaves the power to \me{q-1}, which helps us to drop the absolute value condition when \me{q-1} is even. This condition cannot be applied for \me{q=1} since the rate constraint is eliminated by the differential operation.

By removing the absolute value operator from \eqref{eqn-mse-2}, the problem can be rewritten as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\gamma_{l,k,n}, \mvec{m}{l,k,n}, \\ \beta_{l,k,n}, \alpha_{l,k,n},\delta_{b}, \sigma_{l,k,n}}}{\text{minimize}} &\quad& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \left ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \quad & \nonumber \\
\alpha_{l,k,n} : & \quad & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \quad & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} = t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \quad& \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}. The equality condition is used for \eqref{kkt-mse-1.2} and \eqref{kkt-mse-1.3}, since the variables \me{\epsilon_{l,k,n}} and \me{t_{l,k,n}} are used for the corresponding expressions on the other side.

Now the Lagrangian of the problem expressed in \eqref{kkt-mse-1}, with the corresponding dual variables, is used obtain the \ac{KKT} expressions by partially differentiating with respect to the variables \me{t_{l,k,n}}, \me{\epsilon_{l,k,n}}, \me{m_{l,k,n}}, \me{w_{l,k,n}} and the dual variables \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b}. Since the problem of precoder design using \ac{MSE} reformulation is solved by the iterative method, we use the iteration index \me{i} in the superscript to represent the variables at the respective iteration instants. The discussions on the \ac{KKT} expressions are provided in the  Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, we obtain the following iterative solution with the variables update as
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\alpha^{(i)}_{l,k,n} &=& \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i-1)}} \IEEEyessubnumber \label{kkt-mse-4.1} \\
\sigma_{l,k,n}^{(i)} &=& \dfrac{q \left [ a_k \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i-1)} \right )^{(q-1)} \right ]}{\log(2)} \IEEEyessubnumber \label{kkt-mse-4.2} \\
\mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 + N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2 \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{(x,y) \neq (l,k)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i-1)} \mvec{m}{x,y,n}^{\herm \, (i-1)} \mvec{H}{b_{y},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i-1)}. \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}

The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the \ac{MSE} variables \me{\epsilon_{l,k,n}^{(0)}} and the throughput variables \me{t_{l,k,n}^{(0)}} randomly. It can be initiated by solving \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} for a random transmit precoders \me{\mbf{M}_{k,n}} satisfying \eqref{kkt-mse-1.4}. It can be noted that the proposed iterative algorithm converges faster than the \acl{PD} and the \ac{ADMM} based \acl{DD} scheme, since the later schemes are based on the subgradient approach and the former one achieves the \ac{KKT} points at each iteration. In \eqref{kkt-mse-4}, all expressions provide the closed form solution for the respective variables except the transmit precoders in \eqref{kkt-mse-4.3}, which depends on the variable \me{\delta_b}. It can be seen that the variable \me{\delta_b} are associated only to the \ac{BS} \me{b}, which can be efficiently solved by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. After each iteration instant, the transmit and the receive precoders are exchanged across the coordinating \acp{BS} in \me{\mc{B}} in order to reach the optimal point in the next iteration.

The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{W}{k,n}} evaluated at the receivers. Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{W}{k,n}^{\herm \, (i-1)} \mvec{H}{b,k,n}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}. The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the transmit precoders \me{\mbf{m}^{(0)}_{l,k,n}} randomly satisfying the total power constraint \eqref{kkt-mse-1.4}}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly, \me{\mvec{w}{l,k,n}^{(0)}} with \eqref{kkt-mse-4.6} and \me{{t}_{l,k,n}^{(0)}} using \eqref{kkt-mse-4.5}}
 set the maximum iteration counter \me{I_{\max}} to a valid number \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2} \;
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
	evaluate the receive beamforming vector \me{\mvec{W}{k,n}} by \eqref{kkt-mse-4.6} \;
	exchange the transmit and the receive precoders \me{\mvec{M}{k,n}^{(i)}, \mvec{W}{k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
	$i = i + 1$ \;
  }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
  \label{algo-4}
\end{algorithm}

>>>>

In general, the distributed approaches presented in the earlier sections can be used to perform the precoder design problem in a decentralized way. One significant issue remains in both \acl{PD} and \ac{ADMM} apporaches is the update of the coupling variable. In both the methods, the coupling variables are updated by using the subgradients, which depends on the choice of the step size used for each update. In order to avoid the use of subgradient update for the coupling variables, the \ac{MSE} reformulation approach can be considered by solving the \ac{KKT} equations. Initial work on this approach is discussed extensively in \cite{wmmse_shi} for the \ac{WSRM} problem and \cite{kaleva2012weighted} considered the \ac{WSRM} problem with the additional \ac{QoS} constraints like minimum guaranteed rate requirements.

When the queues are involved, the maximum rate constraint imposed by the number of queued packets at the \ac{BS} poses a nonconvex constraint, which then makes the problem difficult to solve in an iterative manner. But, in our formulation, since the rate constraint imposed by the number of queued packets waiting for the transmission in in the objective function, it provides an efficient apporach to solve the problem with the rate constraints. In this section, we provide an iterative precoder design for the \ac{JSFRA} formulation approached via \ac{MSE} reformulation as discussed in \ref{sec-3.3}. Even though the \ac{JSFRA} scheme using \ac{SCA} approach and the \ac{MSE} reformulation approach obtained the solutions by relaxing the nonconvex constraints by the half spaces, the structure of the \ac{MSE} reformulation problem allows us to decouple the problem readily without further approximations.

In order to come up with the iterative solution, we need to find the \ac{KKT} equations for the the \ac{MSE} reformulation problem defined in \eqref{eqn-mse-2}. It can be seen that the objective function \eqref{eqn-mse-2.1} has the norm function, which requires the sum of absolute values of the vector entries raised to the power \me{q}. Since the absolute of a function is not differentiable, the problem is usually solved by the subgradient approach. Since the subgradients are not unique and the selection of a subgradient and a step size are not guaranteed to be optimal, in this approach, we drop the absolute value operation for the queue deviation function so as to obtain a unique supporting vector. It is valid in the following special cases without affecting the optimal solution
\begin{itemize}
\item when the exponent \me{q} is even or,
\item when the number of backlogged packets for each user is larger than the available resources for the transmission \me{Q_k \gg \sum_{n=1}^N \sum_{l=1}^L {t}_{l,k,n}}.
\end{itemize}
The first condition is required for the iterative design, since the objective function needs to be differentiable to find the \ac{KKT} equations. So, when the exponent \me{q} is even, the absolute operator can be dropped from the objective function without any change in the optimal solution for any number of queued packets.

By removing the absolute value operator from \eqref{eqn-mse-2}, the problem can be rewritten as
\begin{IEEEeqnarray}{rCl}\label{kkt-mse-1}
\underset{\substack{t_{l,k,n},\mvec{M}{k,n}, \alpha_{l,k,n}, \\ \delta_{b},\sigma_{l,k,n},\mvec{W}{k,n}}}{\text{minimize}} &\hspace{0.5cm}& \sum_{b \in \mc{B}} \sum_{k \in \mc{U}_b} \, a_k \, \left ( Q_k - \sum_{n = 1}^N \sum_{l = 1}^{L} t_{l,k,n} \right )^q \IEEEyessubnumber \label{kkt-mse-1.1} \\
\text{subject to} & \hspace{0.5cm} & \nonumber \\
\alpha_{l,k,n} : & \hspace{0.5cm} & \epsilon_{l,k,n} = \left | 1 - \mvec{w}{l,k,n}^\herm \mvec{H}{b_k,k,n} \mvec{m}{l,k,n} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^\herm \mvec{H}{b_y,y,n} \mvec{m}{x,y,n} \right |^2 \\ \nonumber
&\hspace{0.5cm}& \quad {} + N_0 \, \|\mvec{w}{l,k,n}\|^2 \IEEEyessubnumber \label{kkt-mse-1.2} \\
\sigma_{l,k,n} : & \hspace{0.5cm} & - \log(\tilde{\epsilon}_{l,k,n}) - \frac{\left ( {\epsilon}_{l,k,n} - \tilde{\epsilon}_{l,k,n} \right ) }{\tilde{\epsilon}_{l,k,n}} = t_{l,k,n} \, \log(2) \IEEEyessubnumber \label{kkt-mse-1.3} \\
\delta_b : & \hspace{0.5cm} & \sum_{n = 1}^N \sum_{k \in \mathcal{U}_b} \text{tr} \, (\mvec{M}{k,n} \mvec{M}{k,n}^\herm) \leq P_{{\max}}, \fall b, \IEEEyessubnumber \label{kkt-mse-1.4}
\end{IEEEeqnarray}
where \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b} are the dual variables corresponding to the constraints defined in \eqref{kkt-mse-1.2}, \eqref{kkt-mse-1.3} and \eqref{kkt-mse-1.4}. The equality condition is used for \eqref{kkt-mse-1.2} and \eqref{kkt-mse-1.3}, since the variables \me{\epsilon_{l,k,n}} and \me{t_{l,k,n}} are used for the corresponding expressions on the other side.

Now the Lagrangian of the problem expressed in \eqref{kkt-mse-1}, with the corresponding dual variables, is used obtain the \ac{KKT} expressions by partially differentiating with respect to the variables \me{t_{l,k,n}}, \me{\epsilon_{l,k,n}}, \me{m_{l,k,n}}, \me{w_{l,k,n}} and the dual variables \me{\alpha_{l,k,n},\sigma_{l,k,n}} and \me{\delta_b}. Since the problem of precoder design using \ac{MSE} reformulation is solved by the iterative method, we use the iteration index \me{i} in the superscript to represent the variables at the respective iteration instants. The discussions on the \ac{KKT} expressions are provided in the  Appendix \ref{a-1}. Upon solving the \ac{KKT} expressions, we obtain the following iterative solution with the variables update as
\begin{IEEEeqnarray}{rCl} \label{kkt-mse-4}
\alpha^{(i)}_{l,k,n} &=& \dfrac{\sigma_{l,k,n}^{(i)}}{\epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.1} \\
\sigma_{l,k,n}^{(i)} &=& \dfrac{q \left [ a_k \, \left (Q_k - \sum_{n = 1}^N \sum_{l=1}^L t_{l,k,n}^{(i-1)} \right )^{(q-1)} \right ]}{\log(2)}, \IEEEyessubnumber \label{kkt-mse-4.2} \\
\mvec{m}{l,k,n}^{(i)} &=& \left ( \sum_{x \in \mc{U}} \sum_{y=1}^L \alpha_{y,x,n}^{(i)} \mvec{H}{b_k,x,n}^\herm \mvec{w}{y,x,n}^{(i-1)} \mvec{w}{y,x,n}^{\herm \, {(i-1)}} \mvec{H}{b_k,x,n} + \delta_b \mbf{I}_{N_T} \right )^{-1} \alpha^{(i)}_{l,k,n} \mvec{H}{b_k,k,n}^\herm \mvec{w}{l,k,n}^{(i-1)} \IEEEyessubnumber \label{kkt-mse-4.3} \\
\epsilon_{l,k,n}^{(i)} &=& \left | 1 - \mvec{w}{l,k,n}^{\herm \, (i-1)} \mvec{H}{b_k,k,n} \mvec{m}{l,k,n}^{(i)} \right |^2 + \sum_{(x,y) \neq (l,k)} \left | \mvec{w}{l,k,n}^{\mathrm{H} \, (i-1)} \mvec{H}{b_y,y,n} \mvec{m}{x,y,n}^{(i)} \right |^2 \\ \nonumber
&+& \quad  N_0 \, \|\mvec{w}{l,k,n}^{(i-1)}\|^2,\quad \forall k \in \mc{U}, \forall n \in \mc{C} \IEEEyessubnumber \label{kkt-mse-4.4} \\
t_{l,k,n}^{(i)} &=&  -\log_2(\epsilon_{l,k,n}^{(i-1)}) - \frac{\left ( \epsilon_{l,k,n}^{(i)} - \epsilon_{l,k,n}^{(i-1)} \right ) }{\log(2) \, \epsilon_{l,k,n}^{(i-1)}}, \IEEEyessubnumber \label{kkt-mse-4.5} \\
\mvec{w}{l,k,n}^{(i)} &=& \left ( \sum_{(x,y) \neq (l,k)} \mvec{H}{b_y,k,n} \mvec{m}{x,y,n}^{(i-1)} \mvec{m}{x,y,n}^{\herm \, (i-1)} \mvec{H}{b_{y},k,n}^\herm + \mathbf{I}_{N_R} \right ) ^{-1} \; \mvec{H}{b_k,k,n} \; \mvec{m}{l,k,n}^{(i-1)}, \IEEEyessubnumber \label{kkt-mse-4.6}
\end{IEEEeqnarray}
\me{\forall k \in \mc{U}}, \me{\forall n \in \set{1,\ldots,N}} and \me{\forall l \in \set{1,\ldots,L}}.

The \ac{KKT} solutions provided in \eqref{kkt-mse-4} are solved in an iterative manner by initializing the \ac{MSE} variables \me{\epsilon_{l,k,n}^{(0)}} and the throughput variables \me{t_{l,k,n}^{(0)}} randomly. It can be initiated by solving \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} for a random transmit precoders \me{\mbf{M}_{k,n}} satisfying \eqref{kkt-mse-1.4}. It can be noted that the proposed iterative algorithm converges faster than the \acl{PD} and the \ac{ADMM} approach\footnote{from our simulations}, since the later schemes are based on the subgradient approach and the former one achieves the \ac{KKT} points at each iteration. In \eqref{kkt-mse-4}, all expressions provide the closed form solution for the respective variables except the transmit precoders in \eqref{kkt-mse-4.3}, which depends on the variable \me{\delta_b}. It can be seen that the variable \me{\delta_b} are associated only to the \ac{BS} \me{b}, which can be efficiently solved by the bisection method satisfying the power constraint \eqref{kkt-mse-1.4}. After each iteration instant, the transmit and the receive precoders are exchanged across the coordinating \acp{BS} in \me{\mc{B}} in order to reach the optimal point in the next iteration.

The receive beamformers from the users can be informed to the coordinating \acp{BS} by using the precoded uplink pilot signaling, where the precoders used for the uplink pilots are the receive beamformers \me{\mvec{W}{k,n}} evaluated at the receivers. Upon receiving the uplink precoded pilots by the \ac{BS}, the effective channel \me{\mvec{W}{k,n}^{\herm \, (i-1)} \mvec{H}{b,k,n}} can be used in the expression \eqref{kkt-mse-4.3} to update the transmit precoders at the respective \acp{BS} \cite{komulainen2013effective}. The algorithmic representation of the \ac{KKT} based scheme is shown in Algorithm. \ref{algo-4}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=1} and the transmit precoders \me{\mbf{m}^{(0)}_{l,k,n}} randomly satisfying the power constraint \eqref{kkt-mse-1.4}}
 \KwInit{\me{\epsilon_{l,k,n}^{(0)}} randomly, \me{\mvec{w}{l,k,n}^{(0)}} with \eqref{kkt-mse-4.6} and \me{{t}_{l,k,n}^{(0)}} using \eqref{kkt-mse-4.5}}
 set the maximum iteration counter \me{I_{\max}} to a valid number \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
	solve for the dual variables \me{\alpha_{l,k,n}^{(i)}} and \me{\sigma_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.1} and \eqref{kkt-mse-4.2} \;
	update the transmit precoders \me{\mvec{M}{k,n}^{(i)}} with \me{\delta_b} using \eqref{kkt-mse-4.3} by the bisection method satisfying \eqref{kkt-mse-1.4} \;
	update the \ac{MSE} variable \me{\epsilon_{l,k,n}^{(i)}} and the throughput variable \me{t_{l,k,n}^{(i)}} using \eqref{kkt-mse-4.4} and \eqref{kkt-mse-4.5} \;
	evaluate the receive beamforming vector \me{\mvec{W}{k,n}} by \eqref{kkt-mse-4.6} \;
	exchange the transmit and the receive precoders \me{\mvec{M}{k,n}^{(i)}, \mvec{W}{k,n}^{(i)}} across the coordinating \acp{BS} in \me{\mc{B}} \;
	$i = i + 1$ \;
  }
 \caption{\ac{KKT} approach for the \ac{JSFRA} scheme}
  \label{algo-4}
\end{algorithm}

### 2014-07-03 Report/primal_approach_appendix.tex
17.28:00 Jul-03-2014

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the transmit and the receive precoders \me{\mbf{M}_{k,n}} and \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{\ac{PD} based decentralized \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}

>>>>

To obtain the next interference iterate at each \ac{BS}, the locally evaluated dual variables are exchanged among the \acp{BS} in the set \me{\mc{B}} in order to obtain the next interference vector in a distributed manner. Once we obtain the dual variables from all the \acp{BS}, the subgradients relevant to the \ac{BS} \me{b_k} are evaluated by taking the difference between the two \acp{BS} associated with each interference value, \textit{i.e}, \me{s^{\set{b_k}(i)}_{l,k,n,b} = \mu^{\set{b_k}}_{l,k,n} - \mu^{\set{b}}_{l,k,n}}. With the newly estimated subgradient value \me{s^{\set{b_k}(i)}_{l,k,n,b}}, the interference terms corresponding to the \ac{BS} \me{b_k} are updated using \eqref{primal-sg-update}. The algorithmic representation of the \ac{PD} approach is detailed in Algorithm. \ref{algo-2}.
\begin{algorithm}
 \SetAlgoLined
 \DontPrintSemicolon
 \BlankLine
 \SetKwInput{KwInit}{Initialize}
 \KwIn{\me{a_k, \, Q_k, \, \mvec{H}{b,k,n},\; \fall b \in \mathcal{B}, \, \fall k \in \mathcal{U}, \fall n \in \mathcal{C}}}
 \KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall l \in \set{1,2,\dotsc,L}}}
 \KwInit{\me{i=0} and the transmit precoders \me{\tilde{\mbf{m}}_{l,k,n}} randomly satisfying the total power constraint \eqref{eqn-4.3}}
 update \me{\mvec{w}{l,k,n}} with \eqref{eqn-10} and \me{\tilde{\mbf{u}}_{l,k,n}} with \eqref{eqn-8} using \me{\tilde{\mbf{m}}_{l,k,n}} \;
 initialize the interference threshold \me{\zeta_{l,k,n,b}^{\set{0}} \forall b \in \mc{B}, \forall k \in \bar{\mc{U}}_{b_k}, \forall l,n} \;
 for each \ac{BS} \me{b \in \mc{B}}, perform the following procedure \;
 \Repeat{convergence or \me{i \geq I_{\max}}}{
    initialize \me{j=0} \;
    \Repeat{convergence or \me{j \geq J_{\max}}}{
        solve for the transmit precoders \me{\mvec{m}{l,k,n}} and dual variables \me{\mu^{\set{b}}_{l,k,n}} using \eqref{eqn-primal-2} \;
        exchange \me{\mu^{\set{b}}_{l,k,n}} across the coordinating \acp{BS} in \me{\mc{B}} \;
        update \me{\zeta^{\set{b}(j+1)}_{l,k,n,b}} using \eqref{primal-sg-update} locally \;
        \me{j = j + 1} \;
    }
    update the receive beamformers \me{\mvec{w}{l,k,n}} using \eqref{eqn-10} with the recent precoders \me{\mvec{m}{l,k,n}} \;
    exchange the receive precoders \me{\mbf{W}_{k,n}} \me{\forall k \in \mc{U}_b} among the \acp{BS} in \me{\mc{B}} \;
    update \me{\tilde{p}_{l,k,n}}, \me{\tilde{q}_{l,k,n}} and \me{\tilde{\beta}_{l,k,n}} with the recent precoders using \eqref{eqn-wsrm-expr} and \eqref{eqn-6.3} for the \ac{SCA} approach (or) \;
    update \me{\tilde{\epsilon}_{l,k,n}} with the recent precoders using \eqref{eqn-mse-2.3} with equality for the \ac{MSE} formulation approach \;
    $i = i + 1$ \;
  }
 \caption{Decentralization via Primal Decomposition for \acs{JSFRA} scheme}
  \label{algo-2}
\end{algorithm}
